\textcolor{gray}{Our sponsor, HongJing Drive Inc., is a company focusing on full stack supply of autonomous driving. Autonomous driving systems face a multitude of decision problems, including trajectory prediction, motion planning and vehicle control. Using various sensor inputs from cameras, LiDars, and radar, autonomous driving systems are able to identify surrounding objects and make those decisions. Deep learning methods are desirable tools, if not necessary for these perception and control problems. When properly trained with high-quality annotated datasets, deep learning models often yield accurate results that outperform rule-based approaches.}

\textcolor{gray}{However, deep learning tasks need a lot of labeled data for training. Building a large dataset of annotated images with many objects is a costly enterprise. Manual annotation is the most accurate way but it is the least efficient. Fully automatic annotation tool can provide annotations efficiently but with errors and misses that need to be corrected by human, which still requires much labor. Solving the problem jointly by increasing the accuracy and the efficiency of the annotation process is challenging. Existing tools, such as Auto-mage \cite{annomage}, provide limited labeling capacity, such as limited label shape, limited tag hierarchies, and limited suggestions for the tags after pre-processing.}

We, therefore, aims to provide a semi-automated image annotation system for producing a large dataset, which leverage both the accuracy of manual labeling and the efficiency of automatic labeling. This system would help the development of better deep learning models and algorithms and can be extended to different scenes. 



